{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-05 thesis/education.tex
favourably

The survey responses were very positive:
% TODO: corroborate this with snapshot data?
students reported being able both to diagnose and to verify as fixed the vast majority of Landslide's reported bugs,
compared Landslide favorably to stress testing,
and found the experience worthwhile and worth recommending.
Regarding the 100 CPU-hours question in particular,
students could approach answering it in several different ways:
do the three students who answered 20/80 think stress testing is four times as good as Landslide at finding bugs,
or that stress testing requires four times as long to reach the same point of diminishing returns?
On the other extreme, one student said they would spend all 100 CPU-hours on Landslide,
which probably speaks more to their enthusiasm than to a careful attempt to maximize expected number of bugs found
% TODO: put a section reference to future work resource exhaustion / malloc failure injection discussion
(even the author themself recognizes stress testing's advantages for certain types of bugs, such as resource exhaustion).
Nevertheless, the responses' overall bias to spending at least half the CPU-time on Landslide
shows clearly that the students found the experience worthwhile.

>>>>

The survey responses were very positive:
% TODO: corroborate this with snapshot data?
students reported being able both to diagnose and to verify as fixed the vast majority of Landslide's reported bugs,
compared Landslide favourably to stress testing,
and found the experience worthwhile and worth recommending.
Regarding the 100 CPU-hours question in particular,
students could approach answering it in several different ways:
do the three students who answered 20/80 think stress testing is four times as good as Landslide at finding bugs,
or that stress testing requires four times as long to reach the same point of diminishing returns?
On the other extreme, one student said they would spend all 100 CPU-hours on Landslide,
which probably speaks more to their enthusiasm than to a careful attempt to maximize expected number of bugs found
% TODO: put a section reference to future work resource exhaustion / malloc failure injection discussion
(even the author themself recognizes stress testing's advantages for certain types of bugs, such as resource exhaustion).
Nevertheless, the responses' overall bias to spending at least half the CPU-time on Landslide
shows clearly that the students found the experience worthwhile.
